02_LH-SIP_Quantification

### 2022-11-02 02_LH-SIP_Quantification.Rmd
added abundance weighted mean def

    # calculate generation time, converting negatives to zero
    gen_d = turnover_to_gen(u_d),

    # And a memory corrected gen time:
    gen_d_mc = turnover_to_gen(u_d_mc),

@@

```{r}
turnover_summarized <- turnover %>% 
  group_by(
    terrain, 
    inc_time_d,
    compound
  ) %>% 
  dplyr::summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  )

@@

>>>>

@@

```{r}
turnover_summarized <- turnover %>% 
  group_by(
    terrain, 
    inc_time_d,
    compound
  ) %>% 
  dplyr::summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  ) %>% 
  # Calculate generation time based off of mean of replicates
  mutate(
    # calculate generation time, converting negatives to zero
    gen_d = turnover_to_gen(u_d),

    # And a memory corrected gen time:
    gen_d_mc = turnover_to_gen(u_d_mc),
  )

@@

Abundance weighted mean is calculated by:

$$
weighted \space mean = 
\frac{\displaystyle\sum_{i = 1} ^{N} x_{i}w_{i}}{\displaystyle\sum_{i=1} ^{N} x_{i}}
$$

Where $x_i$ is the fractional abundance of compound $i$ and $w_i$ is the relative abundance of compound $i$.
